\ttitle

### 2013-05-18 Appendices/AppendixA-summaries.tex
Summary SVM

\subsection{Perceptron}\label{perceptron}
\subsection{Support Vector Machine}\label{svm-explained}
\subsection{Support Vector Machine Density Functions}\label{svm-pdf}
\subsection{Non-linear models}\label{non-linear}

>>>>

\subsection{Perceptron}\label{perceptron}
Labelled data is \emph{linearly separable} if the exists a linear boundary separating the classes.
The least-squares may find one, but it is not guaranteed.
Image a perfect linearly separatable data set.
Move all the positive points away from the negative, but one.
At one point the new boundary will exclude (misqualify) the one original positive outlier.
The \emph{perceptron} will guaranteed perform perfect separation when the data allows it to be.
It was originally proposed as a \emph{simple neural network}.

\subsection{Support Vector Machine}\label{svm-explained}
\subsection{Support Vector Machine Density Functions}\label{svm-pdf}
\subsection{Non-linear models}\label{non-linear}
